\LARGE \bf Reactive Trajectory Planning and Trajectory Tracking for Pedestrian-Aware Autonomous Driving in Urban Environments

### 2016-01-23 root.tex
overall changes

\author{
  Robert G. Cofield $^{1}$ and
  Rakesh Gupta $^{2}$
  \thanks{
    * This work was performed at Honda Research Institute USA.
  }
  \thanks{
    $^{1}$ Auburn University GAVLab, 1418 Wiggins Hall, Auburn, AL 36832. \textit{robertgcofield@gmail.com}
  }
  \thanks{
    $^{2}$ Honda Research Institute USA Inc, 375 Ravendale Drive, Mountain View, CA 94043. \textit{rgupta@hra.com}
  }
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}

In this paper, we address the problem of trajectory planning for urban roads while reacting to the presence of pedestrians.
Past work reduces jerk and limits velocities and acceleration to smooth trajectories, but it does not consider reactive behaviors such as responding to pedestrians.
On the other hand, systems for collision avoidance plan paths around obstacles and pedestrians, stop for them, or produce a warning. 
In this paper, we present an integrated trajectory generation and tracking system for urban environments that simultaneously considers constraints to maximize human comfort and real-time trajectory updates to react to pedestrians on the road.

Given a desired path, we present a novel online method for planning longitudinal trajectories to follow the urban path with turns and intersections while honoring traffic regulations such as stop signs.
Based on sensor data, our method updates the trajectory plan to safely avoid pedestrians on the road by slowing or stopping.
This is critical in urban environments, when modifying the vehicle's intended path is often not possible.
Our method has closed form solutions, runs at 20 Hz, and is efficient and reliable for use in online planning.
We have confirmed this with a test vehicle and pedestrians with over 100 hours of testing under driverless operation.

@@

When planning trajectories for an autonomous ground vehicle operating on roadways, a typical goal is to minimize navigation time.
It is common to employ the path-velocity decomposition to separate the two tasks so that they can be carried out sequentially or in parallel.
% (i.e., path planning is performed prior to planning the speed that the vehicle will take along the chosen path).
First is Path Planning, which involves computation of the optimal path.
The second task is Trajectory Planning, which involves the computation of the fastest velocity profile that is appropriate for the scenario.

@@

For human passengers, it is widely believed that high levels of jerk (time derivative of acceleration) and high acceleration/velocity values are prime contributors to ride discomfort.
A lot of work has been performed on optimizing these constraints for highways and country roads ~\cite{ziegler14,bahram15,xu12,CHEB15CI}.
Some preliminary work on optimizing these constraints on urban roads has been done ~\cite{Rastelli14,Li15} but they do not consider reactive behavior such as responding to pedestrians or other dynamic objects in the scene.
On the other hand, many systems in the literature find and plan paths around pedestrians, stop for them, or produce a warning ~\cite{pradalier05,benenson06,gu14,mogelmose15,johnson13} but do not work as part of an integrated system that can navigate urban roads.
In this paper, we describe an trajectory generation system that satisfies these constraints for human comfort and is reactive to presence of pedestrians on the road.
%Some work has been done for reacting to pedestrians such as by Singapore groups but it has been done at very low speeds (5 miles/hour).
%There has also been some work in simulating vehicles and modeling uncertainty, but pedestrians are less predictable than cars 
%and can appear suddenly on the road (when someone is jaywalking for example).

In this paper, we present an autonomy framework for pedestrian aware ground vehicles.
Our objective is to travel autonomously from start to destination while honoring traffic laws and avoiding pedestrians on the roadway.
%Desired behavior from the car includes following traffic laws at the intersections such as stop signs.
At stop signs the car should stop and wait for an appropriate amount of time.
It should also react to pedestrians on the road - at intersections as well as on the road.
Pedestrians on the sidewalks should be ignored by the autonomous cars.
Further the pedestrians can be static or moving.
The car should stop, slow down and circum-navigate around pedestrians when appropriate.

Given a desired path, we present a novel method for planning longitudinal trajectories (i.e., the time derivatives of position in the body-forward direction) along that path.
Our method first segments the path using an arbitrary set of kinematic or dynamic constraints which may be functions of the desired path.
Each segment is then planned sequentially by choosing a piecewise constant jerk profile.
The jerk profile is intelligently chosen from a set of pre-solved profiles such that acceleration is continuous and non-infinite throughout the entire path.
The resultant trajectory plan can then be easily sampled to provide a reference for real-time vehicle control, which is called trajectory tracking control.
We present an online method of revising the trajectory plan to safely avoid pedestrians that enter the roadway by slowing or stopping when no alternative paths are available.

We first describe the architecture of our system in Sec. \ref{sec:systemarchirecture}.
We also describe other subsystems that our system needs to work with, and planned stops.
In Section \ref{sec:trajectoryplanning}, we describe trajectory planning which takes a 2D path and generates a trajectory that satisfies jerk and maximum velocity and acceleration constraints. 
We explain how we handle intersections, turns in the road and planned stops due to stop signs (that have already been marked in the map).
We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once a trajectory plan is formulated, it must be utilized online to send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking problem, which is discussed in Section \ref{sec:trajectorytracking}.
Section V describes the high level Path Manager that calls the trajectory planner as necessary to 
exhibit reactionary behavior and stop for pedestrians that may appear on the road.
We then conclude and discuss future extensions.
% tracking

@@

Our system architecture is shown in Figure \ref{fig:addreact}.
There are 4 primary input components: a path planner, navigation filter, pedestrian detector, and a map which provides the location of stop signs.
% nav filter
For navigation filtering we use an ADMA-G  commercial automotive GPS/INS system.
It receives RTK corrections via cell modem.
It outputs global position, global heading, body frame velocity and body frame acceleration to centimeter level accuracy.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/MissingReactionPiece2.png}
  \caption{
   Primary system components. The ``Path Manager'' and ``Trajectory Planner'' scomponents (in blue) are presented herein.
  }
  \label{fig:addreact}
\end{figure}

Pedestrian detection is performed via a camera and LiDAR system based on \cite{Gepperth2013,Gepperth2014}.
It computes a bounding box for each pedestrian as shown in Figure \ref{fig:ped}.
The pedestrian position is transformed to the vehicle body frame, and subsequently transformed to global frame to be related to the planned path.

@@

We assume that we have access to a path planner.
For example, this can be a service similar to Google Maps except that it provides lane level maps. 
We assume that the path planner operates independently from the trajectory planner and tracker.
We also assume that we have a high resolution digital map with lane centers, stop signs, crosswalk geometry, and turning curves at intersections.
The destination is manually input into the system by the passengers.
Using the path planner, we obtain a path along lane centers from the vehicle's current location (computed by the navigation filter) to the destination.
This plan is output as set of global waypoints, with the waypoints corresponding to stop signs flagged.
This same map database is used to search for stop signs and provide their locations.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.3\columnwidth]{graphics/IntersectionCrosswalks.png}
  \caption{
    A car turning right at the intersection only needs to consider pedestrians in the pedestrian crossings shown yellow.
    Pedestrians in the green crossings can be ignored unless they appear somewhere on the road.
  }
  \label{fig:intersect}
\end{figure}

@@

Beyond the input subsystems, there are three other major components: a high-level planner, a low-level planner, and a software controller which governs engine speed, braking, and steering.
The controller takes as an input a trajectory which is sampled at 10 Hz and spans 2 seconds, beginning at the moment of data transmission.
This short-term trajectory is oriented in the vehicle body frame.
\textbf{Citation for controller ????}.

The high-level planner is referred to as the ``path manager'', and performs decision-making as well as governing operation of the low-level planner.
Its primary functions are:
\begin{enumerate}
  \item Stop the vehicle at stop signs and wait until the assosciated intersection is clear before continuing.
  \item Reactively reduce speed or stop altogether for pedestrians which pose a collision risk, then continue when they are clear.
  \item Govern the trajectory planner.
\end{enumerate}
The low-level planner is referred to as the ``trajectory planner'', and is responsible for quantifying the actions dictated by the path manager.
Its primary functions are:
\begin{itemize}
  \item Compute medium-range trajectories for a given path.
  \item Revise trajectories to react to pedestrians.
  \item Sample the current trajectory for input to the controller.
\end{itemize}
This work focuses on the path manager (Sec. \ref{sec:pathmanager}) and the trajectory planner (Sec. \ref{sec:trajectoryplanning} \& Sec. \ref{sec:trajectorytracking}).

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/StateMachineSimple.png}
  \caption{State Transition Diagram}
  \label{fig:st}
\end{figure}

Many systems perform trajectory planning over a sliding window within the full path which progresses with the vehicle.
This requires ... \textbf{something about computing actions through stop signs before it's necessary and how that's inefficient}.
We propose to break the path into sub-paths at each stop location which is known a priori, as shown in Fig. \ref{fig:subpathdivision}, and  execute them incrementally.

In the absence of pedestrians, the path manager cycles between PSTOP and NORMAL states.
In NORMAL state, the path manager send the first subpath to the trajectory planner, which then plans and executes it before coming to a stop at the end of the subpath.
In PSTOP mode, the path manager waits for a pre-set time duration before returning to NORMAL mode, where the next subpath is executed.
When pedestrians are present, the transition from PSTOP to NORMAL is delayed until there are no pedestrians detected in the range denoted by $\Delta s_{resume}$.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{
    Dividing the path into subpaths at stop signs.
    The trajectory generation is serially called on each segment which is colored differently here.
  }
  \label{fig:subpathdivision}
\end{figure}

All detected pedestrians locations are compared against the high-resolution digital map, so that pedestrians which are not on the roadway or near an upcoming crosswalk are not considered.
Then each pedestrian location is projected onto the total path in the same manner as described in Sec. \ref{sec:trajectorytracking}.
Pedestrians which are on a different subpath than the vehicle are disregarded, as well as those which are behind the vehicle (i.e., $s_{ped} < s_{veh}$).
All the pedestrians which remain pose a potential collision risk, however only the closest is considered for RSTOP.

@@

Next the nominal distance needed to stop $\Delta s_{RSTOP}$ must be computed given the vehicle's current location, speed, and forward acceleration.
The procedure for doing this will be the same as the procedure for planning the RSTOP trajectory later with a few steps omitted, since the planning algorithm is extremely efficient.

Note that a static buffer distance, $\Delta s_{buf}$ is added to ensure safety and comfort.
RSTOP is triggered when $\Delta s_{RSTOP} + \Delta s_{buf} >= s_{ped} - s_{veh}$ and the actual available stopping distance $\Delta s_{avail} = s_{ped} - s_{veh}$ is computed.
Planning and executing the trajectory for coming to a halt is detailed in Sec. \ref{sec:reactivestoptrajectory}.

This procedure is repeated when the nearest pedestrian location changes by a value more than some static buffer $\Delta s_{replan} < \Delta s_{buf}$ compared to the location for which the current RSTOP planned.
This value is typically set to 1 meter.
Normal operation is resumed when the distance between the vehicle and the closest detected pedestrian satisfies $s_{ped} - s_{veh} > \Delta s_{resume} + \Delta s_{RSTOP}$. The static resume buffer should be set such that $\Delta s_{resume} > \Delta s_{buf} + \Delta s_{replan}$.
The preceding quantities are depicted graphically in Fig. \ref{fig:react}.

@@

The task trajectory planning in this context is to take a 2 dimensional (horizontal plane) set of waypoints from the path manager, and compute a series of constant jerk intervals for motion along the length of the path.
This trajectory must be time optimal yet still fall within constraints on speed, acceleration, and jerk.
Elevation changes will not be addressed here.
Integrating piecewise constant jerk over time yields acceleration which is piecewise linear over time, speed which is piecewise quadratic over time, and position which is piecewise cubic over time.

Prescribed initial and end conditions for position, speed, and acceleration must also be honored.
All planning is longitudinal; that is, speed is the primary focus, and we assume that the control subsystem will ensure that the vehicle follows the prescribed path.
This means that the desired trajectory plan may be mapped into one dimension using curvilinear coordinates to significantly simplify the solution.
We show how two dimensional concerns (specifically cornering speeds for this work) are expressed in one dimension to guide planning.

@@

Our approach to fitting appropriate jerk profiles to complex subpaths is to further break each subpath into segments which have very simple shape.
Once this is done, each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment will be defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ for must be defined for each segment.

The segmentation process proceeds as follows:
\begin{enumerate} \label{asdf}
  \item \emph{Ceiling calculation}, where $v_m$, $\mathbf{a}_m$, and $\mathbf{j}_m$ are found for every point in the given subpath.
  \item \emph{Clustering}, in which subpath points are grouped sequentially and the segment boundaries are determined..
  \item \emph{Consolidation}, in which a single $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described in Section \ref{sec:jerkprofiles} may be applied to each of the segments so that a plan of jerk vs. time may be generated.

The ceiling calculation is a minimax problem.
Each of the 9 scalars is a minimum of several maxima computed from an arbitrary set of constraints.
For instance, acceleration constraints may include a set of limits derived from friction coefficients at every point along the subpath.

% How we actually did this.
For the purposes of developing a simple example application, two constraints will be used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_k}$ for $k = 1, ..., N_p$, where $N_p$ is the number of waypoints in the subpath.
The value $\kappa_k$ denotes the path curvature at each point.
For each pathpath point, the value $v_{m,k}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$.

@@

\begin{figure}[thpb]
  \centering
  \subfigure[
    Result of dividing a single subpath into separate segments.
    The clustering algorithm used here sets segments boundaries before and after curves.
    The subpath segments in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.176 m/s (25 mi/hr).
  ]{
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  \subfigure[
    Example of how the subpath's segment boundaries are determined, as well as how $v_m$ is consolidated to determine the speed ceiling for each segment.
    The x-axis corresponds to distance along the subpath above.
    The legal speed limit of 11.176 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling is shown in blue.
  ]{
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{Dividing a subpath into segments and determining speed ceilings for each segment.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

% need better notation here.
In the consolidation step, a single set of $\mathbf{g}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ must be calculated for each segment using the values corresponding to each of the waypoints which comprise the segment in question.
The minimum of scalar across all constituent points is chosen.
While not time optimal, it does ensure that no constraints are violated while still keeping the number of total segments low.
In the present example, this means that in the straight portions of the subpath $v_m = SL$ and in the curves $v_m$ is set to the value required to obtain $a_{B,y}^{max}$ for the entirety of the curve.
As a result, many of the curves will have a constant speed.
For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are initially all set constant for the entire path, using values from \cite{Maurya2012,Hoberock1977,Long2000}.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/Full7PhaseSpecVertical.png}
  \caption{
    7 phase constant jerk profile along curvilinear distance axis.
    All values needed to completely parameterize a single path segment for trajectory are labeled here.}
  \label{fig:full7phasespec}
\end{figure}

@@

There are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
We propose to define 4 other basic profiles, and our algorithm judiciously chooses the appropriate profile for every segment defined by a vector $\mathbf{b}$.
The other profiles are explained below in Section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_k, k = 1 ... N_s$ and can be solved individually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

>>>>

\author{
  Robert G. Cofield$^{1}$ and
  Rakesh Gupta$^{2}$
  \thanks{
    * This work was performed at Honda Research Institute USA.
  }
  \thanks{
    $^{1}$ Auburn University GAVLab, 1418 Wiggins Hall, Auburn, AL 36832. \textit{robertgcofield@gmail.com}
  }
  \thanks{
    $^{2}$ Honda Research Institute USA Inc, 375 Ravendale Drive, Mountain View, CA 94043. \textit{rgupta@hra.com}
  }
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
In this paper, we address the problem of trajectory planning for urban roads while reacting to the presence of pedestrians.
Past work reduces jerk and limits velocities and acceleration to smooth trajectories, but it does not consider reactive behaviors such as responding to pedestrians.
On the other hand, systems for collision avoidance plan paths around obstacles and pedestrians, stop for them, or produce a warning. 
In this paper, we present an integrated trajectory generation and tracking system for urban environments that simultaneously considers constraints to maximize human comfort and real-time trajectory updates to react to pedestrians on the road.

Given a desired path, we present a novel online method for planning longitudinal trajectories to follow the urban path with turns and intersections while honoring traffic regulations such as stop signs.
Based on sensor data, our method updates the trajectory plan to safely avoid pedestrians on the road by slowing down or stopping.
This is critical in urban environments, when modifying the vehicle's intended path is often not possible.
Our method has closed form solutions, runs at 20 Hz, and is efficient and reliable for use in online planning.
We have confirmed this with a test vehicle and pedestrians with over 100 hours of testing under driverless operation.

@@

When planning trajectories for an autonomous ground vehicle operating on roadways, a typical goal is to minimize navigation time.
It is common to employ the Path-Trajectory decomposition to separate the two tasks so that they can be carried out sequentially or in parallel.
% (i.e., path planning is performed prior to planning the speed that the vehicle will take along the chosen path).
First is {\it Path Planning}, which involves computation of the optimal path.
The second task is {\it Trajectory Planning}, which involves the computation of the fastest velocity profile that is appropriate for the scenario.

@@

For human passengers, it is widely believed that high levels of jerk (time derivative of acceleration) and high acceleration/velocity values are prime contributors to ride discomfort.
A lot of work has been performed on optimizing these constraints for highways and country roads ~\cite{ziegler14,bahram15,xu12,CHEB15CI}.
Some preliminary work on optimizing these constraints on urban roads has been done ~\cite{Rastelli14,Li15} but they do not consider reactive behavior such as responding to pedestrians or other dynamic objects in the scene.
On the other hand, many systems in the literature find and plan paths around pedestrians, stop for them, or produce a warning ~\cite{pradalier05,benenson06,gu14,mogelmose15,johnson13} but do not work as part of an integrated system that can navigate urban roads.
In this paper, we describe a trajectory generation system that satisfies these constraints for human comfort and is reactive to presence of pedestrians on the road.
%Some work has been done for reacting to pedestrians such as by Singapore groups but it has been done at very low speeds (5 miles/hour).
%There has also been some work in simulating vehicles and modeling uncertainty, but pedestrians are less predictable than cars 
%and can appear suddenly on the road (when someone is jaywalking for example).

We present an autonomy framework for pedestrian-aware ground vehicles.
Our objective is to travel autonomously from start to destination while honoring traffic laws and avoiding pedestrians on the roadway.
%Desired behavior from the car includes following traffic laws at the intersections such as stop signs.
At stop signs the car should stop and wait for an appropriate amount of time.
It should also react to pedestrians - at intersections as well as on the road.
Pedestrians on the sidewalks should be ignored by the autonomous car.
Further, the pedestrians can be static or moving.
The car should stop, slow down and go around pedestrians when appropriate.

Given a desired path, we present a novel method for planning longitudinal trajectories (i.e., the time derivatives of position in the body-forward direction) along that path.
Our method first segments the path using an arbitrary set of kinematic or dynamic constraints which may be functions of the desired path.
Each segment is then planned sequentially by choosing a piecewise constant jerk profile.
The jerk profile is intelligently chosen from a set of pre-solved profiles such that acceleration is continuous and non-infinite throughout the entire path.
The resultant trajectory plan can then be easily sampled to provide a reference for real-time vehicle control, which is called trajectory tracking control.
We present an online method of revising the trajectory plan to safely avoid pedestrians that enter the roadway by slowing down or stopping when no alternative paths are available.

We first describe the architecture of our system in Sec. \ref{sec:systemarchirecture}.
We also describe other subsystems that our system needs to work with, and planned stops.
Section \ref{sec:pathmanager} describes the high level Path Manager that calls the trajectory planner as necessary to 
exhibit reactive behavior and stop for pedestrians that may appear on the road.
In Section \ref{sec:trajectoryplanning}, we describe trajectory planning which takes a 2D path and generates a trajectory that satisfies maximum velocity, acceleration and jerk constraints. 
We explain how we handle intersections, turns in the road and planned stops due to stop signs (that have already been marked in the map).
We then describe extensions to trajectory planner that handle reactivity to pedestrians in the environment. 
Once a trajectory plan is formulated, it must be utilized online to send the reference signal to the controllers that govern steering, braking, and engine speed.
This is the trajectory tracking problem, which is discussed in Section \ref{sec:trajectorytracking}.
We then conclude and discuss future extensions.
% tracking

@@

Our system architecture is shown in Figure \ref{fig:addreact}.
There are 4 primary input components: Navigation Filter, Pedestrian Detector, a Path Planner, and a Map which provides the location of stop signs.
% nav filter
For navigation filtering we use an ADMA-G  commercial automotive GPS/INS system.
It receives RTK corrections via cell modem.
It outputs global position, global heading, body frame velocity and body frame acceleration to centimeter level accuracy.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/MissingReactionPiece2.png}
  \caption{
   Primary system components. The {\it Path Manager} and {\it Trajectory Planner} components (in blue) are presented herein.
   \textbf{RG: blue color is too dark to read text ????????????}
  }
  \label{fig:addreact}
\end{figure}

Pedestrian detection is performed via a camera and LiDAR system based on \cite{Gepperth2013,Gepperth2014}.
It computes a bounding box for each pedestrian as shown in Figure \ref{fig:ped}.
The pedestrian position is computed in the vehicle body frame, and subsequently transformed to global frame to be related to the planned path.

@@

We assume that we have access to a path planner.
For example, this can be a service similar to Google Maps except that instead of road level route, it provides lane level route. 
We assume that the path planner operates independently from the trajectory planner and tracker.
We also assume that we have a high resolution digital map with lane centers, stop signs, crosswalk geometry, and turning curves at intersections.
The destination is manually input into the system by the passengers.
Using the path planner, we obtain a path along lane centers from the vehicle's current location (computed by the navigation filter) to the destination.
This plan is output as a set of global waypoints, with the waypoints corresponding to stop signs flagged.
This same map database is used to search for stop signs and provide their locations.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.3\columnwidth]{graphics/IntersectionCrosswalks.png}
  \caption{
    A car turning right at the intersection only needs to consider pedestrians in the pedestrian crossings shown in yellow.
    Pedestrians at the green crossings can be ignored unless they appear somewhere on the road.
  }
  \label{fig:intersect}
\end{figure}

@@

Beyond these input subsystems, our system has three major components: a High-Level Planner, a Low-Level Planner, and a Software Controller.

The high-level planner is referred to as the {\it Path Manager}, and performs decision-making as well as governing operation of the low-level planner.
Its primary functions are:
\begin{enumerate}
  \item Stop the vehicle at stop signs and wait until the associated intersection is clear before continuing.
  \item Reactively reduce speed or stop altogether for pedestrians which pose a collision risk, then continue when they are clear.
  \item Govern the Trajectory Planner.
\end{enumerate}
The low-level planner is referred to as the {\it Trajectory Planner}, and is responsible for quantifying the actions dictated by the Path Manager.
Its primary functions are:
\begin{itemize}
  \item Compute medium-range trajectories for a given path.
  \item Revise trajectories to react to pedestrians.
  \item Sample the current trajectory for input to the controller.
\end{itemize}

The Software Controller governs engine speed, braking, and steering.
The controller takes as an input a trajectory which is sampled at 10 Hz and spans 2 seconds, beginning at the moment of data transmission.
This short-term trajectory is oriented in the vehicle body frame.
\textbf{Citation for controller ????}.
This work focuses on the Path Manager (Sec. \ref{sec:pathmanager}) and the Trajectory Planner (Sec. \ref{sec:trajectoryplanning} \& Sec. \ref{sec:trajectorytracking}).

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/StateMachineSimple.png}
  \caption{State Transition Diagram for ?????????? more detail????? }
  \label{fig:st}
\end{figure}

Many systems perform trajectory planning over a sliding window within the full path which progresses with the vehicle.
This requires ... \textbf{something about computing actions through stop signs before it's necessary and how that's inefficient}.
We propose to break the path into sub-paths at each stop location which is known a priori, as shown in Fig. \ref{fig:subpathdivision}, and call Trajectory Planner for each sub-path incrementally.

In the absence of pedestrians, the path manager cycles between NORMAL and PSTOP states.
In NORMAL state, the path manager send the first subpath to the trajectory planner, which then plans and executes it before coming to a stop at the end of the subpath.
In PSTOP mode, the path manager waits for a pre-set time duration before returning to NORMAL mode, where the next subpath is executed.
When pedestrians are present, the transition from PSTOP to NORMAL is delayed until there are no pedestrians detected in the range denoted by $\Delta s_{resume}$.

\begin{figure}[thpb]
  \centering
  \includegraphics[width=0.5\columnwidth]{graphics/Subpaths.png}
  \caption{
    Dividing the path into sub-paths at stop signs.
    The trajectory generation is serially called on each sub-path which are colored differently here.
  }
  \label{fig:subpathdivision}
\end{figure}

All detected pedestrian locations are compared against the high-resolution digital map, so that pedestrians that are not on the roadway or near an upcoming crosswalk are not considered.
Then each pedestrian location is projected onto the total path in the same manner as described in Sec. \ref{sec:trajectorytracking}.
Pedestrians that are on a different subpath than the vehicle are disregarded, as well as those which are behind the vehicle (i.e., $s_{ped} < s_{veh}$).
All the remaining pedestrians pose potential collision risks, however only the closest pedestrian is considered for RSTOP.

@@

When a pedestrian is detected, the nominal distance needed to stop, $\Delta s_{RSTOP}$, must be computed given the vehicle's current location, speed, and forward acceleration.
The procedure for doing this is the same as the procedure for planning the RSTOP trajectory later with a few steps omitted, since the planning algorithm is extremely efficient.

Note that a static buffer distance, $\Delta s_{buf}$ is added to ensure safety and comfort.
RSTOP is triggered when $\Delta s_{RSTOP} + \Delta s_{buf} >= \Delta s_{avail}$ and the actual available stopping distance $\Delta s_{avail} = s_{ped} - s_{veh}$ is computed.
Planning and executing the trajectory for coming to a halt is detailed in Sec. \ref{sec:reactivestoptrajectory}.

This procedure is repeated when the nearest pedestrian location changes by a value more than some static buffer $\Delta s_{replan} < \Delta s_{buf}$ compared to the location for which the current RSTOP planned.
$\Delta s_{replan}$ value is typically set to 1 meter.
Normal operation is resumed when the distance between the vehicle and the closest detected pedestrian satisfies $s_{ped} - s_{veh} > \Delta s_{resume} + \Delta s_{RSTOP}$. The static resume buffer should be set such that $\Delta s_{resume} > \Delta s_{buf} + \Delta s_{replan}$.
The preceding quantities are depicted graphically in Fig. \ref{fig:react}.

@@

The task of Trajectory Planning is to take a 2 dimensional (horizontal plane) set of waypoints from the Path Manager, and compute a series of constant jerk intervals for motion along the length of the path.
This trajectory must be time optimal yet still fall within constraints on speed, acceleration, and jerk.
Elevation changes will not be addressed here.
Integrating piecewise constant jerk over time yields acceleration which is piecewise linear over time, speed which is piecewise quadratic over time, and position which is piecewise cubic over time.

Prescribed initial and end conditions for position, speed, and acceleration must be honored.
All planning is longitudinal; that is, speed is the primary focus, and we assume that the control subsystem will ensure that the vehicle follows the prescribed path.
This means that the desired trajectory plan may be mapped into one dimension using curvilinear coordinates to significantly simplify the solution.
We show how two dimensional \textbf{concerns????} (specifically cornering speeds for this work) are expressed in one dimension to guide planning.

@@

Our approach to fitting appropriate jerk profiles to complex sub-paths is to further break each subpath into segments which have very simple shape.
Once this is done, each segment can be compared to a library of possible jerk profiles to find a good match.
Each segment will be defined by the vector $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
Additionally, the desired positive and negative acceleration $\mathbf{a}_m = [a^+_m , a^-_m]$ and the desired positive and negative jerk $\mathbf{j}_m = [j^+_m , j^-_m]$ for must be defined for each segment.

The segmentation process proceeds as follows:
\begin{enumerate} \label{asdf}
  \item \emph{Ceiling calculation}, where 
%$v_m$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
initial/final speeds, speed limit, peak acceleration and jerk 
are found for every point in the given subpath.
  \item \emph{Clustering}, in which subpath points are grouped sequentially and the segment boundaries are determined..
  \item \emph{Consolidation}, in which a single $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ is selected for each segment.
\end{enumerate}
After this is done, the process described in Section \ref{sec:jerkprofiles} may be applied to each of the segments so that a plan of jerk vs. time may be generated.

The ceiling calculation is a minimax problem.
Each of the 9 scalars \textbf{RG: please explain 9 scalars ???} is a minimum of several maxima computed from an arbitrary set of constraints.
For instance, acceleration constraints may include a set of limits derived from friction coefficients at every point along the subpath.

% How we actually did this.
For the purposes of developing a simple example application, two constraints will be used for $v_{m}$: legal speed limit $SL$ and lateral acceleration limit $a_{B,y}^{max}$. 
Lateral acceleration constraints are translated into longitudinal speed constraints using the approximation $v_{m,k}(a_{B,y}) = \sqrt{a_{B,y}^{max}/\kappa_k}$ for $k = 1, ..., N_p$, where $N_p$ is the number of waypoints in the subpath.
The value $\kappa_k$ denotes the path curvature at each point.
For each \textbf{??? sub-path ??} point, the value $v_{m,k}(a_{B,y}^{max})$ denotes the speed necessary to obtain the limit lateral acceleration, denoted by $a^{max}_{B,y}$.

@@

\begin{figure}[thpb]
  \centering
  \subfigure[
    Result of dividing a single subpath into separate segments.
    The clustering algorithm used here sets segments boundaries before and after curves.
    The subpath segments in red indicate areas where the longitudinal speed required to adhere to lateral acceleration limits is below the legal speed limit of 11.176 m/s (25 mi/hr).
  ]{
    \includegraphics[width=0.8\columnwidth]{graphics/course_highlighted_turns.png}
  }
  \\
  \subfigure[
    Example of how the sub-path's segment boundaries are determined, as well as how $v_m$ is consolidated to determine the speed ceiling for each segment.
    The x-axis corresponds to distance along the subpath above.
    The legal speed limit of 11.176 m/s (25 mi/hr) is shown in cyan.
    The longitudinal speed required to adhere to lateral acceleration limits is shown in red.
    The resultant speed ceiling is shown in blue.
  ]{
  \includegraphics[width=0.8\columnwidth]{graphics/speed_ceiling.png}
  }
  \caption{Dividing a subpath into segments and determining speed ceilings for each segment.}
  \label{fig:1Dto2DandSegmentation}
\end{figure}

% need better notation here.
In the consolidation step, a single set of 
%$\mathbf{g}$, $\mathbf{a}_m$, and $\mathbf{j}_m$ 
initial/final speeds, speed limit, peak acceleration and jerk 
must be calculated for each segment using the values corresponding to each of the waypoints which comprise the segment in question.
The minimum of scalar across all constituent points is chosen.
While not time optimal, it does ensure that no constraints are violated while still keeping the number of total segments low.
In the present example, this means that in the straight portions of the subpath $v_m = SL$ and in the curves $v_m$ is set to the value required to obtain $a_{B,y}^{max}$ for the entirety of the curve.
As a result, many of the curves will have a constant speed.
For the sake of simplicity, the values of $a^+_{m,k}$, $a^-_{m,k}$, $j^+_{m,k}$, and $j^-_{m,k}$ are initially all set constant for the entire path, using values from \cite{Maurya2012,Hoberock1977,Long2000}.

@@

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/Full7PhaseSpecVertical.png}
  \caption{
    7-phase constant jerk profile along curvilinear distance axis.
    All values needed to completely parameterize a single path segment for trajectory are labeled here.}
  \label{fig:full7phasespec}
\end{figure}

@@

There are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
We propose to define 4 other basic profiles, and our algorithm judiciously chooses the appropriate profile for every segment defined by a vector $\mathbf{b}$.

\textbf{RG: does not belong here: The other profiles are explained below in Section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_k, k = 1 ... N_s$ and can be solved individually in sequence. Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}. }

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\mathbf{b}$.
All impossible scenarios are automatically ruled out (e.g., end speed above speed limit, traveling speed of zero, negative speeds in $\mathbf{b}$, etc).
It should be noted that traveling backward (i.e., in reverse gear) is not supported in this work.
To find closed-form solutions for each, a symbolic solver is used.
The target values for each profile are the time steps between jerk changes.
These are solved by plugging in $\mathbf{b}$, $\mathbf{a}_m$, and $\mathbf{j}_m$.
